The Practical Application of Computerised Multistage Tests

### 2021-03-04 article.Rmd
Add sample data (trial-data.csv)

```{r module items, echo=TRUE}
# create a function to map module names to indices
moduleIndices <- seq(1:7)
names(moduleIndices) <- c("A", "B", "C", "D", "E", "F", "G")
module <- function(n) { unname(moduleIndices[n]) }

@@

We define the `mstDesign()` function to generate the set of test designs we want to investigate. This function varies the number of items for each module by stage and can be repeatedly applied to the set of designs in the `stages` list. It effectively generates variants of the test design presented above in \@ref(module difficulties).

@@

  itembank <- rbind(genDichoMatrix(stage[1], model = "1PL", bPrior = c("norm", 0.0, 1)),
                    genDichoMatrix(stage[2], model = "1PL", bPrior = c("norm", -1.0, 1)),
                    genDichoMatrix(stage[2], model = "1PL", bPrior = c("norm", 1.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", -1.5, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", -0.5, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", 0.5, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", 1.5, 1)))
  itembank <- as.matrix(itembank)

@@

# create a composite data frame and plot the alphas and the number of samples
# we'll want to focus on modules that show a low alpha and a small number of samples
# as we may want to get more trial data for these, or look at the items to make
# sure they are testing the right skill (or both)
module <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')
stage <- c(1, 2, 2, 3, 3, 3, 3)
alpha <- c(alphasModuleA$alpha, alphasModuleB$alpha, alphasModuleC$alpha,
            alphasModuleD$alpha, alphasModuleE$alpha, alphasModuleF$alpha,
            alphasModuleG$alpha)
num_items <- c(alphasModuleA$p, alphasModuleB$p, alphasModuleC$p,
            alphasModuleD$p, alphasModuleE$p, alphasModuleF$p,
            alphasModuleG$p)
num_responses <- c(alphasModuleA$n, alphasModuleB$n, alphasModuleC$n,
            alphasModuleD$n, alphasModuleE$n, alphasModuleF$n,
            alphasModuleG$n)

dfCronbachsAlpha <- data.frame(module, stage, num_items, num_responses, alpha)

@@

ggplot(dfCronbachsAlpha, aes(x=alpha, y=num_responses, size = num_items, color = module)) +
    geom_point() +
    scale_x_continuous(limits = c(0, 1)) +
    theme(legend.position = "right") +
    labs(x = "alpha", y = "# responses") +
    geom_vline(xintercept = 0.7, linetype="dotted")
```
Ideally we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same trait. This measure is really only useful as a guide for further investigations; the ultimate decision on whether to modify the items in each module should be taken in collaboration with the subject matter experts.

>>>>

```{r module items, echo=TRUE}
# create a function to map module names to indices
moduleIndices <- seq(1:7)
moduleNames <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')
names(moduleIndices) <- moduleNames
module <- function(n) { unname(moduleIndices[n]) }

@@

We define the `mstDesign()` function to generate the set of test designs we want to investigate. This function varies the number of items for each module by stage and can be repeatedly applied to the set of designs in the `stages` list. It effectively generates variants of the test design presented above in \@ref(module difficulties) for 3-stage designs.

@@

  itembank <- rbind(genDichoMatrix(stage[1], model = "1PL", bPrior = c("norm", 0.0, 1)),
                    genDichoMatrix(stage[2], model = "1PL", bPrior = c("norm", -2.0, 1)),
                    genDichoMatrix(stage[2], model = "1PL", bPrior = c("norm", 2.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", -3.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", -1.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", 1.0, 1)),
                    genDichoMatrix(stage[3], model = "1PL", bPrior = c("norm", 3.0, 1)))
  itembank <- as.matrix(itembank)

@@

# create a composite data frame and plot the alphas and the number of samples
# we'll want to focus on modules that show a low alpha and a small number of samples
# as we may want to get more trial data for these, or look at the items to make
# sure they are testing the right skill (or both)
stage <- c(1, 2, 2, 3, 3, 3, 3)
alpha <- c(alphasModuleA$alpha, alphasModuleB$alpha, alphasModuleC$alpha,
            alphasModuleD$alpha, alphasModuleE$alpha, alphasModuleF$alpha,
            alphasModuleG$alpha)
num_items <- c(alphasModuleA$p, alphasModuleB$p, alphasModuleC$p,
            alphasModuleD$p, alphasModuleE$p, alphasModuleF$p,
            alphasModuleG$p)
num_responses <- c(alphasModuleA$n, alphasModuleB$n, alphasModuleC$n,
            alphasModuleD$n, alphasModuleE$n, alphasModuleF$n,
            alphasModuleG$n)

dfCronbachsAlpha <- data.frame(moduleNames, stage, num_items, num_responses, alpha)

@@

ggplot(dfCronbachsAlpha, 
       aes(x=alpha, y=num_responses, size = num_items, color = moduleNames)) +
    geom_point() +
    scale_x_continuous(limits = c(0, 1)) +
    theme(legend.position = "right") +
    labs(x = "alpha", y = "# responses") +
    geom_vline(xintercept = 0.7, linetype="dotted")
```
Ideally we're looking for alphas of 0.7 and above; less than this indicates that there is weak covariance between the items in the module, which means they may not be testing the same trait. This measure is really only useful as a guide for further investigations; the ultimate decision on whether to modify the items in each module should be taken in collaboration with the subject matter experts.
